Specifying BYOD Policies with Authorization Logic

### 2016-03-10 paper.tex
language tool rules

Other similarities appear when looking at how devices connect to networks.
The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks (though again it does not specify what \emph{secure} actually means). 
In contrast the SANS policy says what security features are required and that, whilst secured access points are preferred, an open access point may be used with a VPN as a last resort.
\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks.''}]
'edinburgh-policy' says Device canConnectTo(AP) if AP isSecure.
\end{lstlisting}
\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``If mobile workers do require connectivity through public, open, or untrusted WLAN, then users MUST use WLANs using, if available and in this order: WPA(2) encryption, WEP 256 bits (or 128 bits), or finally open networks if nothing else is available. Users connected to data networks in an open environment MUST use a VPN connection.''}]
'sans-policy' says Device canConnectTo(AP) if AP isSecure.
'sans-policy' says AP isSecure if AP canUseWPA2.
'sans-policy' says AP isSecure if AP canUseWEP256.
'sans-policy' says AP isSecure if AP canUseWEP128.
'sans-policy' says Device canConnectTo(AP) if Device hasVPN(VPN) where connect(VPN) = true.
\end{lstlisting}
By analysing the similarities in policies a framework of BYOD predicates could be defined that would allow policies to be compared \emph{precisely} using standard terms.

@@

\bibitem{Abadi:2003kta}
M. Abadi.
\newblock {Logic in access control},
\newblock {\em Logic in Computer Science}, 2003.

>>>>

Other similarities appear when looking at how devices connect to networks.
The Edinburgh policy recommends disabling automatic access to open unsecured Wi-Fi networks (though again it does not specify what \emph{secure} actually means). 
In contrast, the SANS policy says what security features are required and that, whilst secured access points are preferred, an open access point may be used with a VPN as a last resort.
\begin{lstlisting}[title={\footnotesize\textbf{Edinburgh}:~\itshape ``Control your devices connections by disabling automatic connection to open, unsecured Wi-Fi networks.''}]
'edinburgh-policy' says Device canConnectTo(AP) if AP isSecure.
\end{lstlisting}
\begin{lstlisting}[title={\footnotesize\textbf{SANS}:~\itshape ``If mobile workers do require connectivity through public, open, or untrusted WLAN, then users MUST use WLANs using, if available and in this order: WPA(2) encryption, WEP 256 bits (or 128 bits), or finally open networks if nothing else is available. Users connected to data networks in an open environment MUST use a VPN connection.''}]
'sans-policy' says Device canConnectTo(AP) if AP isSecure.
'sans-policy' says AP isSecure if AP canUseWPA2.
'sans-policy' says AP isSecure if AP canUseWEP256.
'sans-policy' says AP isSecure if AP canUseWEP128.
'sans-policy' says Device canConnectTo(AP) if Device hasVPN(VPN) where connect(VPN) = true.
\end{lstlisting}
By analysing the similarities in policies a framework of BYOD predicates could be defined that would allow policies to be compared \emph{precisely} using standard terms.

@@

\bibitem{Abadi:2003kta}
M. Abadi.
\`newblock {Logic in access control},
\newblock {\em Logic in Computer Science}, 2003.
